\textls[-15]{\thetitle \mbox{(Technical Report)}}

### 2022-07-27 syntax.tex
Reply the comments.

Now, together with sealing, we can read \ruleref{Sig Add} and
\ruleref{Lnkg Add} out clearly: given a constructed linkage $o : \cL\sigma$
of signature $\sigma$, the next added field $t : T$ will have
to be in the context of the abstraction $A$\YZ{Why do Lnkg Add and Sig Add leave A unspecified? I thought this A corresponds to 'self'.}\EDJreply{It is not unspecified. I now change it so that it is more clear. It is parametric as well. Just note that when specifying the abstraction `A', the seal `f' has to be specified at the sametime. (Thus I omitted it initially because it is implicitly specified w.r.t. the speicifcation of `f') }\YZreply{
  Changed what? I think Lnkg Add and Sig Add were not changed.
  I still don't see how sealing converts \cC \{a : \bW sigma ; ..\} to \cC\{a : \cU ; ..\}
  and how the latter is now used as the abstracted A.
}
of the compilation $\cC\sigma$ (witnessed by the seal $f$).
The ``concatenation'' of the
$o$ and $t$ leads to a new linkage, of which the signature is the
``concatenation'' of the $\sigma$ and $T$ (we also record the sealing
$f$ for simplicity). The key here is our signature, will \textit{record}
this abstraction witness $f$,\YZ{Why is it necessary to record the witness f? I don't see how p_f nu is needed anywhere.}
thus any projected member will still be in
the abstracted context and thus possibly \textit{inheritable}.  The
construction of linkage in \ruleref{Lnkg Add} requires $t$ to
\textbf{only} refer to the (abstraction $A$ of) former part of the
defining family $o : \cL\sigma$, this is to avoid inconsistency
mentioned in \ref{chg:consistency} in metatheory.

@@

$$
\Rule[name=Hdler]
{\goodType{\Gamma}{A}{}
\quad \goodType{\Gamma, A}{B}{}
\quad \goodType{\Gamma}{R}{}
}
{\goodType{\Gamma}{"RecSig1"~A~B~R \equiv (\Pi A (\Pi (\Pi B (R[\pi_1\circ\pi_1])) R[\pi_1\circ\pi_1]) )}{}}
\quad 
\Rule[name=Hdlers]
{\goodWSig{\Gamma}{\sigma}{n}
\quad \goodType{\Gamma}{R}{}
}
{\goodSig{\Gamma}{"RecSig"~\sigma~R}{n}}
$$
$$
\Rule[name=Hdler-Proj]
{ \goodWSig{\Gamma}{\sigma}{N}
\quad \goodTerm{\Gamma}{o}{\cL("RecSig"~\sigma~R)}
\quad n < N
}
{\goodTerm{\Gamma}{"prjR"~n~o}{("RecSig1"~(\pi_1^n \sigma)~(\pi_2^n \sigma)~R)[\pi_1]}}
$$
$$
\Rule[name=Rec-Constr]
{ \goodWSig{\Gamma}{\sigma}{N}
\quad \goodType{\Gamma}{T}{\bW \sigma}
\quad \goodType{\Gamma}{R}{}
\quad \goodTerm{\Gamma}{r}{\cL("RecSig"~\sigma~R)}
\quad \goodTerm{\Gamma}{w}{El~("W"~T)}
}
{\goodTerm{\Gamma}{"Wrec"~r~w}{R}}\YZ{
(1) Use \tau for inductive types and \sigma for linkage signatures.
(2) Try using the same metavariables (j and n) as in the rules on W-types.
(3) In Rec-Constr, no checking of \Gamma \vdash T : \bW \tau?
(4) Why are RecSig1, RecSig, Wrec, prjR not listed in the syntax figure?
}
$$

>>>>

Now, together with sealing, we can read \ruleref{Sig Add} and
\ruleref{Lnkg Add} out clearly: given a constructed linkage $o : \cL\sigma$
of signature $\sigma$, the next added field $t : T$ will have
to be in the context of the abstraction $A$\YZ{Why do Lnkg Add and Sig Add leave A unspecified? I thought this A corresponds to 'self'.}\EDJreply{It is not unspecified. I now change it so that it is more clear. It is parametric as well. Just note that when specifying the abstraction `A', the seal `f' has to be specified at the sametime. (Thus I omitted it initially because it is implicitly specified w.r.t. the speicifcation of `f') }\YZreply{
  Changed what? I think Lnkg Add and Sig Add were not changed.
  I still don't see how sealing converts \cC \{a : \bW sigma ; ..\} to \cC\{a : \cU ; ..\}
  and how the latter is now used as the abstracted A.
}\EDJreply{I added the $\goodType{\Gamma}{A}{}$  as you suggested. 
\cC \{a : \bW sigma ; ..\} is definitionally equal to a sigma type as Compile rule suggested. 
If you expand the definition, you will see two sigma type. 
You are asking where is the function \cC \{a : \bW sigma ; ..\} to \cC\{a : \cU ; ..\}, which by definition is requesting (Sigma (a : \bW sigma ; ..)) to (Sigma (a : \cU ; ..)). 
This is something doable in vanilla MLTT, with the help of transforming \bW sigma to \cU, by rule `Ind-Type'. }
of the compilation $\cC\sigma$ (witnessed by the seal $f$).
The ``concatenation'' of the
$o$ and $t$ leads to a new linkage, of which the signature is the
``concatenation'' of the $\sigma$ and $T$ (we also record the sealing
$f$ for simplicity). The key here is our signature, will \textit{record}
this abstraction witness $f$,\YZ{Why is it necessary to record the witness f? I don't see how p_f nu is needed anywhere.}\EDJreply{1. this is for the sake of eta/beta rule (local soundness + local completeness); 2.It is actually used in the rule Compile (the last one), if Ct is compile a variable, then the f will be replace by p_f}
thus any projected member will still be in
the abstracted context and thus possibly \textit{inheritable}.  The
construction of linkage in \ruleref{Lnkg Add} requires $t$ to
\textbf{only} refer to the (abstraction $A$ of) former part of the
defining family $o : \cL\sigma$, this is to avoid inconsistency
mentioned in \ref{chg:consistency} in metatheory.

@@

$$
\Rule[name=Hdler]
{\goodType{\Gamma}{A}{}
\quad \goodType{\Gamma, A}{B}{}
\quad \goodType{\Gamma}{R}{}
}
{\goodType{\Gamma}{"RecSig1"~A~B~R \equiv (\Pi A (\Pi (\Pi B (R[\pi_1\circ\pi_1])) R[\pi_1\circ\pi_1]) )}{}}
\quad 
\Rule[name=Hdlers]
{\goodWSig{\Gamma}{\sigma}{n}
\quad \goodType{\Gamma}{R}{}
}
{\goodSig{\Gamma}{"RecSig"~\sigma~R}{n}}
$$
$$
\Rule[name=Hdler-Proj]
{ \goodWSig{\Gamma}{\sigma}{N}
\quad \goodTerm{\Gamma}{o}{\cL("RecSig"~\sigma~R)}
\quad n < N
}
{\goodTerm{\Gamma}{"prjR"~n~o}{("RecSig1"~(\pi_1^n \sigma)~(\pi_2^n \sigma)~R)[\pi_1]}}
$$
$$
\Rule[name=Rec-Constr]
{ \goodWSig{\Gamma}{\sigma}{N}
\quad \goodTerm{\Gamma}{T}{\bW \sigma}
\quad \goodType{\Gamma}{R}{}
\quad \goodTerm{\Gamma}{r}{\cL("RecSig"~\sigma~R)}
\quad \goodTerm{\Gamma}{w}{El~("W"~T)}
}
{\goodTerm{\Gamma}{"Wrec"~r~w}{R}}\YZ{
(1) Use \tau for inductive types and \sigma for linkage signatures.
(2) Try using the same metavariables (j and n) as in the rules on W-types.
(3) In Rec-Constr, no checking of \Gamma \vdash T : \bW \tau?
(4) Why are RecSig1, RecSig, Wrec, prjR not listed in the syntax figure?
}\EDJreply{Thx. Working on it. I seem to forgot to add inheritance as well.}
$$
